%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------


\cvsection{Interests}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}
%---------------------------------------------------------
  \cvskill
    {Cooking} % Interest
    {I love cooking for family \& friends. I am a savvy home cook with proper knife skills and enjoy Persian \& Asian cooking, baking, pizzas, sandwiches, and omelets.} % Description

%---------------------------------------------------------
  \cvskill
    {Photography} % Interest
    {Since high school, I have enjoyed the art of photography. I started with film media through graduate school, where I took extracurricular black \& white film development courses and switched to digital format circa 2010. These days I shoot with my iPhone or mirrorless camera, and some of my images are on my \href{https://flickr.com/photos/cambysese/}{flickr} and \href{https://instagram.com/ktavabi}{Instagram} blogs.} % Description
%---------------------------------------------------------
  \cvskill
    {Calisthenics} % Interest
    {I have been a yoga practitioner since college and enjoy the challenge of calisthenic exercises and unconventional weight strengthening with, e.g., kettlebells, Indian or Gada clubs to improve overall fitness.} % Description
%---------------------------------------------------------
  \cvskill
    {Video Games} % Interest
    {I have been an avid video gamer since the days of Super Mario Brothers on the original Nintendo console. I enjoy gaming with my daughter on the Xbox, Playstation, and PC platforms.} % Description
%---------------------------------------------------------
  \cvskill
    {Swimming} % Interest
    {I have enjoyed swimming for as long as I can remember, and these days I enjoy going on long open water swims in Lake Washington, or any lake for that matter, during the hot summer days.} % Description
%---------------------------------------------------------

\end{cvskills}